% Section 1 - Game Overview

\section{Game Overview}

\subsection{Game Concept}
    \begin{adjustwidth}{1.5em}{0pt}
    This is an isometric turn based tactics game. In this game players will control small armies of 4 champions under a commander. With these armies players will do battle on various battlegrounds in action packed turn based combat. Champions will move around directly on the field of battle and deal with enemies by means of attacks, abilities and spells. The commander on the other hand is a unit that is not on the field of battle but will assist the champions via means of buffs or damaging spells depending on your choice of commander. Battlegrounds are small symmetrical or asymmetrical grids that can consist of multiple layers, no more than 2, and predictable hazards. Players will go back and forth controlling their champions based on a predetermined initiative values, which determine at what point in the turn the champion is allowed to move. Commander buffs and spells however can be used when ever player gains control of one of their champions. The objective is to defeat all enemy champions.
    \end{adjustwidth}

\subsection{Feature Set}
    \begin{adjustwidth}{1.5em}{0pt}
    This game will feature a diverse cast of champions and commanders for the player to choose from. The game will also include multiple battle grounds to do battle on. Along with a practice arena and peer vs. peer ranking system.
    \end{adjustwidth}

\subsection{Genre}
    \begin{itemize}
        \item [-] Turn Based Strategy
        \item [-] Fantasy
        \item [-] Multiplayer
    \end{itemize}

\subsection{Target Audience}
    \begin{adjustwidth}{1.5em}{0pt}
    Teens and up that are interested in competitive turn based strategy games.
    \end{adjustwidth}

\subsection{Game Flow Summary}
% How does the player move through the game. Both through framing interface and the game itself.

\subsection{Look and Feel}
% What is the basic look and feel of the game? What is the visual style?

\subsection{Project Scope}
% A summary of the scope of the game.

\subsubsection{Art and Asset Scope}

\subsubsection{Number of Planned Levels}

\subsubsection{Number of Planned Heroes}

\newpage